Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-19 vesicle_code/docs/adhesion/adhesion.tex
edits through out

Also the dip at the edge of contact region is
related to (but different from) the buckling of membrane under strong
adhesion: A closer inspection on the dip at the edge shows that the
membrane distance is smaller than the neutral separation distance
$\delta$ there for more deflated vesicles.
For $\triangle A =0.6$ and $0.75$  the adhesion force is mostly attractive
 in the contact region except at the edge, where the adhesive
force turns repulsive.  For $\triangle A=0.95$, however, the adhesion force is mostly repulsive,
leading to large tension in the rest of the vesicle membrane.

@@

  \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image01.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image02.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image03.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image04.png}
  \includegraphics[height = 0.2\textwidth,trim={3.5cm 0cm 0cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image05.png}
  \caption{\label{fig:extensionalNonsymmetric}Dynamics of a vesicle pair
  in a planar extensional flow. ${\cal H} = 0.7$ for the first three
  rows, and ${\cal H}=0.6$ for the bottom row. From top to bottom, the
  initial vertical displacement $\triangle y=0$, 0.02, 0.1 and 0.1. The
  reduced area is $\Delta A = 0.75$, the extension rate $\dot\epsilon=
  0.09$ and the adhesion distance $\delta = 0.4$.  The color coding is
  the tension.}
  \end{figure}

The hydrodynamics of a single vesicle in an extensional flow has
revealed novel nonlinear vesicle dynamics not found for a viscous
drop~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  Here we focus on a
planar extensional flow  where the fluid velocity field $\uu=\dot\epsilon(-x,y)$ is centered at the 
the origin ($(x,y)=(0,0)$), the stagnation point where the fluid flow converges horizontally and diverges vertically.
Placed symmetrically at the stagnation point of an extensional flow,
a single vesicle may remain steady and symmetric for low extension rate $\dot\epsilon$.
For sufficiently large extension rate $\dot\epsilon$ the vesicle may undergo asymmetric deformation \cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}, 
similar to a surfactant-laden viscous drop under a planar extensional flow \cite{JanssenBoonAgterof1997_AIChE,HuPineLeal2000_PoF}.
To our knowledge no studies on the interactions between two vesicles in an extensional flow are available in the literature.
In the following we first illustrate how two vesicles interact with each other in a planar extensional flow. We then illustrate how the adhesion strength between membranes can be
measured non-intrusively by using the fluid trap.

%To investigate how two vesicles interact with each other in a planar extensional flow,
At the beginning of the first set of simulations (left panels in Figure~\ref{fig:extensionalNonsymmetric})
we place a vesicle at $(x,y)=(0,0)$, 
and the other vesicle at $(x,y) = (3,\triangle y)$ where the initial vertical displacement $\triangle y$ varies from
$\triangle y=0$ for the top row, $\triangle y = 0.02$ for the second row, to
$\triangle y =0.1$ for the bottom two rows in Figure~\ref{fig:extensionalNonsymmetric}.
The adhesion strength ${\cal H} = 0.7$ for the top three rows, and ${\cal H} =0.6$ for the bottom row.
The color coding is the membrane tension with the color bar on the right of each row. We note that the negative tension in an
extensional flow is consistent with the tension for a vesicle with finite bending forces \cite{Narsimhan2014_JFM} and the
speculation for a wrinkled membrane in the elongational flow \cite{KantslerSegreSteinberg2007_PRL}.

Once the planar extensional flow is turned on at $t=0^+$, two vesicles move
towards each other  as shown in  Figure \ref{fig:extensionalNonsymmetric}.
For $\triangle y=0$ in the top row, the two vesicles stay on the $x$-axis as they move closer to 
form a doublet. We observe that the left vesicle (initially centered at $(0,0)$) moves to the left due to the impinging
vesicle from the right. As time progresses they form a doublet
and reach a steady configuration that is symmetric with respect to the stagnation point 
(square marks in the top row of Figure \ref{fig:extensionalNonsymmetric}).

For $\triangle y>0$ we observe similar vesicle dynamics only at the beginning 
when the right vesicle moves towards the stagnation point and the left vesicle is pushed to the left of the stagnation point. 
As both vesicles come to close vicinity of the stagnation point, the elevated right vesicle ($\triangle y >0$) is pulled up by the diverging flow in the $y$ direction,
causing rotation of both vesicles. 
We also observe that the larger the initial vertical displacement, the larger the rotation and the faster both vesicles move
away from the stagnation point.
%
For sufficiently strong adhesion (${\cal H}=0.7$ for the first three rows in Figure \ref{fig:extensionalNonsymmetric}),
 the two vesicles rotate and move away from the stagnation point as a doublet until the end of simulations ($t=100$).
As the two vesicles move further away from the stagnation point, the extensional flow becomes more effective in pulling the two drops apart
as shown in the third row of Figure \ref{fig:extensionalNonsymmetric}.
For ${\cal H}=0.6$ (bottom row in Figure \ref{fig:extensionalNonsymmetric})  
the two vesicles are separated by the diverging flow as early as $t=75$, and are clearly not a doublet at the end of simulation.

Two main observations can be made of results in Figure~\ref{fig:extensionalNonsymmetric}:
(1) The membrane tension is highly non-uniform on the vesicles, leading to a significant Marangoni stress along the membrane as in the case of a surfactant-laden drop
at the center of an extensional flow. Thus it is reasonable to expect that the flow around the vesicles is significantly altered.
(2) In an extensional flow vesicles are prone to move away from the stagnation point.
A small initial vertical displacement $\triangle y$ in one  of the vesicles causes both vesicles to not only rotate but also move away from the
center. Once vesicles move off the horizontal axis, their hydrodynamics is dominated by the diverging flow as they move further away.
Thus in the microfluidic experiment it is often more desirable to trap the vesicle around the center of an extensional flow \cite{Spjut2010_MSThesis_Chapter3}.
%
With an active
control algorithm to place the stagnation point at a desirable location
by adjusting the flow with a feedback
loop~\cite{BentleyLeal1986_JFMa,Johnson-Chavarria2011_EMJ}, a particle can be trapped at the
stagnation point for long time scales to facilitate image acquisition or
other detailed measures such as particle image velocimetry of flow
inside and around the particle.

@@

\begin{figure}[htp]
  \begin{tabular}{@{}p{0.3\linewidth}@{\quad}p{0.3\linewidth}@{\quad}p{0.3\linewidth}@{}}
  \subfigimg[width=\linewidth]{(a)}{figs/rotate1.pdf} &
  \subfigimg[width=\linewidth]{(b)}{figs/angleDefinition.pdf} &
  \subfigimg[width=\linewidth]{(c)}{figs/rotate2.pdf}
  \end{tabular}
%   \includegraphics[width=0.25\textwidth]{figs/rotate1.pdf}
%   \hspace{20pt}
%   \includegraphics[width=0.25\textwidth]{figs/angleDefinition.pdf}
%   \hspace{20pt}
%   \includegraphics[width=0.25\textwidth]{figs/rotate2.pdf}
   \caption{\label{fig:InclinationAngle} The definition of the
   inclination angle of a vesicle doublet at the center of an
   extensional flow.  An inclination angle of $\pi$ indicates a doublet
   whose long axis is orthogonal to the diverging direction, while an
   inclination angle of $\pi/2$ indicates a doublet whose short axis is
   orthogonal to the diverging direction.  The square mark is a
   stagnation point and the round point is located at the center of the
   vesicle.  The initial configurations in this section all have an
   inclination angle of $\theta = \pi$.}
 \end{figure}

Based on how the contact region aligns with the extensional flow, we can
define the inclination angle $\theta$ of the vesicle doublet as illustrated in
Figure~\ref{fig:InclinationAngle}(b). When $\theta=\pi$ (Figure~\ref{fig:InclinationAngle}(a))
the diverging flow
pulls the vesicles apart from each other and the attractive adhesion
force is essential to keep the two vesicles from separating.  In
contrast, when $\theta = \pi/2$ (Figure~\ref{fig:InclinationAngle}(c)), 
%the doublet long axis is aligned with the diverging flow, 
the converging flow pushes the vesicles towards
each other and the repulsive force is essential to keep the
two vesicles at the separation distance.  With the converging flow
pushing the two vesicles towards the stagnation point dynamically placed
at the doublet center, we expect the $\theta=\pi/2$ configuration to be more stable
than the $\theta=\pi$ configuration. 
%
%This is because when $\theta=\pi$
%the diverging flow is pulling the vesicles away from each other as shown
%in the illustration.  However, when the doublet inclination angle is
%fixed at $\theta=\pi/2$, the vesicle doublet stays intact if the
%adhesive force is strong enough to dominate the fluid drag.  However, it
%is possible that the diverging flow may overcome adhesion and break up
%the doublet.  It is also reasonable to expect a vesicle doublet to
%rotate from the less stable configuration $\theta=\pi$ to the more
%stable configuration $\theta=\pi/2$, so that the fluid flow is pushing
%them together rather than pulling them apart.

@@

In the following numerical experiments we initially place a vesicle
doublet with $\theta=\pi$, so that the diverging flow may be strong
enough to pull vesicles away from the doublet.  At low extension
rates, we expect the doublet to stay bound at the fluid trap stagnation
point.  On the other hand, the vesicle doublet may become unstable and
eventually separate at higher extension rates.  Thus we expect there
to exist a critical extension rate $\dot\epsilon_c$ above which the vesicle
doublet cannot stay bound under a given adhesion potential.  Therefore,
the dependence of the critical extension rate $\dot\epsilon_c$ on the adhesion
potential and the mechanical vesicle properties provides a means to
probe the physics of membrane adhesion.

@@

Figure~\ref{fig:extensional1} shows snapshots from simulating a vesicle doublet of reduced area  $\Delta A = 0.7$
at three different extension rates. A general feature of the doublet dynamics is that the doublet rotates from
$\theta=\pi$ configuration towards the more stable $\theta=\pi/2$
configuration.  
%
We also
observe that with moderate extension rates, the doublet falls short of
aligning their long axis with the diverging direction.  Moreover, the
final inclination angle is closest to the stable $\theta=\pi/2$ for the
smallest extension rates. While this doublet remains bound for all
the considered extension rates, a doublet with a reduced area of
$\Delta A = 0.8$ is split with a critical extension rate $\dot\epsilon_c =
0.1$ (Figure~\ref{fig:extensional3}).

@@

%
The equilibrium configuration for low extension rate $\dot\epsilon=0.02$ (top row in Figure~\ref{fig:extensional1}) is
almost identical to the equilibrium configuration for $\triangle y=0$ (top row of  Figure~\ref{fig:extensionalNonsymmetric}).
The rotation of the vesicle doublet 
from $\theta=\pi$ to $\theta=\pi/2$ can be understood as the transition from an unstable configuration $\theta=\pi$ to a stable configuration $\theta=\pi/2$.
For higher extension rates (second and third rows in Figure~\ref{fig:extensional1}) the partially rotated vesicle pairs at equilibrium are
also very similar to the case of $\triangle y=0.02$ (second row of Figure~\ref{fig:extensionalNonsymmetric}).
Such asymmetric vesicle configuration is reminiscent of the asymmetric deformation of a single vesicle in an extensional flow \cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}.
To gain more insight into such nonlinear dynamics, in the following we explore more physical characterization of the transition from $\theta=\pi$ to $\theta=\pi/2$ at
different reduced area and extension rate.
%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a planar shear flow}
\label{sec:sflow} 
We consider two vesicles suspended in the planar shear flow $\uu =
\dot\gamma(y,0)$, where $\dot\gamma$ is the shear rate.  To be
consistent with simulations in previous sections, the vesicles have a
length of $2\pi$ for all reduced areas.  The initial placement of the
vesicles is chosen so that the flow dives them towards one another in a
head-on collision.  In the absence of adhesion, once the vesicles are
sufficiently close, they are deflected to opposite sides of the $y$
axis, pass one another, and then separate.  However, in the presence of
adhesion, the vesicles can form a doublet for certain values of the
separation distance $\delta$, Hamaker constant $\mathcal{H}$, shear rate
$\dot\gamma$, and reduced area $\Delta A$.  If a doublet does form, then
it undergoes a periodic motion with a period that depends on the same
parameters.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{sec:conclusions}}
In this work we use a boundary integral formulation with adaptive
time-stepping to simulate hydrodynamics of two vesicles with adhesive
interactions.  In a quiescent flow, two vesicles that are initially
sufficiently far apart move towards each other under a long-range
attraction.  We use a lubrication theory to estimate the time required
to reach the separation distance $\delta$, and the theoretical scaling
is in good agreement with numerical results.  Once two membranes are
within separation distance $\delta$, the adhesive force turns repulsive
and the membranes flatten to form a contact region.  Our simulations
show that the membranes in the contact region are actually curved with
end points at the shortest distance.  Once a vesicle doublet forms, we
examine the dependence of membrane bending and adhesion energies on the
reduced area, the Hamaker constant, and the separation distance.

>>>>

Also the dip at the edge of contact region is
related to (but different from) the buckling of membrane under strong
adhesion: A closer inspection on the dip at the edge shows that the
membrane distance is smaller than the neutral separation distance
$\delta$ there for more deflated vesicles.
For $\Delta A =0.6$ and $0.75$  the adhesion force is mostly attractive
 in the contact region except at the edge, where the adhesive
force turns repulsive.  For $\Delta A=0.95$, however, the adhesion force is mostly repulsive,
leading to large tension in the rest of the vesicle membrane.

@@

  \includegraphics[height = 0.2\textwidth,trim={1cm 0cm 1cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image01.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image02.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image03.png}
  \includegraphics[height = 0.2\textwidth,trim={4cm 0cm 4cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image04.png}
  \includegraphics[height = 0.2\textwidth,trim={3.5cm 0cm 0cm 0cm},clip]
    {figs/extensional_displacement1em1_adS6em1_tension_image05.png}
  \caption{\label{fig:extensionalNonsymmetric}Dynamics of a vesicle pair
  in a planar extensional flow. The Hamaker constant is ${\cal H} = 0.7$
  for the first three rows, and ${\cal H}=0.6$ for the bottom row. From
    top to bottom, the initial vertical displacement is $\Delta y=0$,
    $0.02$, $0.1$, and $0.1$. The reduced area is $\Delta A = 0.75$, the
    extension rate $\dot\epsilon= 0.09$, and the adhesion distance
    $\delta = 0.4$.  The color coding is the tension.}
  \end{figure}

The hydrodynamics of a single vesicle in an extensional flow has
revealed novel nonlinear vesicle dynamics not found for a viscous
drop~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  Here we focus on
a planar extensional flow  where the fluid velocity field
$\uu=\dot\epsilon(-x,y)$ is centered at the origin ($(x,y)=(0,0)$), the
stagnation point where the fluid flow converges horizontally and
diverges vertically.  Placed symmetrically at the stagnation point of an
extensional flow, a single vesicle may remain steady and symmetric for
low extension rate $\dot\epsilon$.  For sufficiently large extension
rate $\dot\epsilon$ the vesicle may undergo asymmetric
deformation~\cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt},
similar to a surfactant-laden viscous drop under a planar extensional
flow~\cite{JanssenBoonAgterof1997_AIChE,HuPineLeal2000_PoF}.  To our
knowledge no studies on the interactions between two vesicles in an
extensional flow are available in the literature \todo[inline]{Something
is off with this sentence}.  In the following we first illustrate how
two vesicles interact with each other in a planar extensional flow. We
then illustrate how the adhesion strength between membranes can be
measured non-intrusively by using the fluid trap.

At the beginning of the first set of simulations (left panels in
Figure~\ref{fig:extensionalNonsymmetric}) we place a vesicle at
$(x,y)=(0,0)$, and the other vesicle at $(x,y) = (3,\Delta y)$ where
the initial vertical displacement $\Delta y$ varies from $\Delta
y=0$ for the top row, $\Delta y = 0.02$ for the second row, to
$\Delta y =0.1$ for the bottom two rows in
Figure~\ref{fig:extensionalNonsymmetric}.  The Hamaker constant is ${\cal
H} = 0.7$ for the top three rows, and is ${\cal H} =0.6$ for the bottom
row.  The color coding is the membrane tension with the color bar on the
right of each row. We note that the negative tension in an extensional
flow is consistent with the tension for a vesicle with finite bending
forces~\cite{Narsimhan2014_JFM} and the speculation for a wrinkled
membrane in the elongational flow~\cite{KantslerSegreSteinberg2007_PRL}.

Once the planar extensional flow is turned on at $t=0^+$, two vesicles
move towards each other as shown in
Figure~\ref{fig:extensionalNonsymmetric}.  For $\Delta y=0$ in the top
row, the two vesicles stay on the $x$-axis as they move closer to form a
doublet.  We observe that the left vesicle (initially centered at
$(0,0)$) moves to the left due to the impinging vesicle from the right.
As time progresses they form a doublet and reach a steady configuration
that is symmetric with respect to the stagnation point (square marks in
the top row of Figure~\ref{fig:extensionalNonsymmetric}).

For $\Delta y>0$ we observe similar vesicle dynamics only at the
beginning when the right vesicle moves towards the stagnation point and
the left vesicle is pushed to the left of the stagnation point.  As both
vesicles come to close vicinity of the stagnation point, the elevated
right vesicle ($\Delta y > 0$) is pulled up by the diverging flow in the
$y$ direction, causing rotation of both vesicles.  We also observe that
the larger the initial vertical displacement, the larger the rotation
and the faster both vesicles move away from the stagnation point. For
sufficiently strong adhesion (${\cal H}=0.7$ for the first three rows in
Figure~\ref{fig:extensionalNonsymmetric}), the two vesicles rotate and
move away from the stagnation point as a doublet until the end of
simulations ($t=100$).  As the two vesicles move farther away from the
stagnation point, the extensional flow becomes more effective in pulling
the two drops apart as shown in the third row of
Figure~\ref{fig:extensionalNonsymmetric}.  For ${\cal H}=0.6$ (bottom
row in Figure~\ref{fig:extensionalNonsymmetric})  the two vesicles are
separated by the diverging flow as early as $t=75$, and are clearly not
a doublet at the end of simulation.

Two main observations that can be drawn from the results in
Figure~\ref{fig:extensionalNonsymmetric} are: (1) The membrane tension is
highly non-uniform on the vesicles, leading to a significant Marangoni
stress along the membrane as in the case of a surfactant-laden drop at
the center of an extensional flow. Thus it is reasonable to expect that
the flow around the vesicles is significantly altered.  (2) In an
extensional flow, vesicles are prone to move away from the stagnation
point.  A small initial vertical displacement $\Delta y$ in one  of the
vesicles causes both vesicles to not only rotate but also move away from
the center. Once vesicles move off the horizontal axis, their
hydrodynamics is dominated by the diverging flow as they move farther
away.  Thus in the microfluidic experiment it is often more desirable to
trap the vesicle around the center of an extensional
flow~\cite{Spjut2010_MSThesis_Chapter3}. With an active control
algorithm to place the stagnation point at a desirable location by
adjusting the flow with a feedback
loop~\cite{BentleyLeal1986_JFMa,Johnson-Chavarria2011_EMJ}, a particle
can be trapped at the stagnation point for long time scales to
facilitate image acquisition or other detailed measures such as particle
image velocimetry of flow inside and around the particle.

@@

\begin{figure}[htp]
  \begin{tabular}{@{}p{0.3\linewidth}@{\quad}p{0.3\linewidth}@{\quad}p{0.3\linewidth}@{}}
  \subfigimg[width=\linewidth]{(a)}{figs/rotate1.pdf} &
  \subfigimg[width=\linewidth]{(b)}{figs/angleDefinition.pdf} &
  \subfigimg[width=\linewidth]{(c)}{figs/rotate2.pdf}
  \end{tabular}
%   \includegraphics[width=0.25\textwidth]{figs/rotate1.pdf}
%   \hspace{20pt}
%   \includegraphics[width=0.25\textwidth]{figs/angleDefinition.pdf}
%   \hspace{20pt}
%   \includegraphics[width=0.25\textwidth]{figs/rotate2.pdf}
   \caption{\label{fig:InclinationAngle} The definition of the
   inclination angle of a vesicle doublet at the center of an
   extensional flow.  An inclination angle of $\pi$ indicates a doublet
   whose long axis is orthogonal to the diverging direction, while an
   inclination angle of $\pi/2$ indicates a doublet whose short axis is
   orthogonal to the diverging direction.  The square mark is a
   stagnation point and the round point is located at the center of the
   vesicle.  The initial configurations in this section all have an
   inclination angle of $\theta = \pi$.}
   \todo[inline]{What do you think about reversing (a) and (b)?}
 \end{figure}

Based on how the contact region aligns with the extensional flow, we can
define the inclination angle $\theta$ of the vesicle doublet as
illustrated in Figure~\ref{fig:InclinationAngle}(b). When $\theta=\pi$
(Figure~\ref{fig:InclinationAngle}(a)) the diverging flow pulls the
vesicles apart from each other and the attractive adhesion force is
essential to keep the two vesicles from separating.  In contrast, when
$\theta = \pi/2$ (Figure~\ref{fig:InclinationAngle}(c)), the converging
flow pushes the vesicles towards each other and the repulsive force is
essential to keep the two vesicles at the separation distance.  With the
converging flow pushing the two vesicles towards the stagnation point
dynamically placed at the doublet center, we expect the $\theta=\pi/2$
configuration to be more stable than the $\theta=\pi$ configuration. 
%
%This is because when $\theta=\pi$ the diverging flow is pulling the
%vesicles away from each other as shown in the illustration.  However,
%when the doublet inclination angle is fixed at $\theta=\pi/2$, the
%vesicle doublet stays intact if the adhesive force is strong enough to
%dominate the fluid drag.  However, it is possible that the diverging
%flow may overcome adhesion and break up the doublet.  It is also
%reasonable to expect a vesicle doublet to rotate from the less stable
%configuration $\theta=\pi$ to the more stable configuration
%$\theta=\pi/2$, so that the fluid flow is pushing them together rather
%than pulling them apart.

@@

\todo[inline]{Bryan is here}
In the following numerical experiments we initially place a vesicle
doublet with $\theta=\pi$, so that the diverging flow may be strong
enough to pull vesicles away from the doublet.  At low extension rates,
we expect the doublet to stay bound at the fluid trap stagnation point.
On the other hand, the vesicle doublet may become unstable and
eventually separate at higher extension rates.  Thus we expect there to
exist a critical extension rate $\dot\epsilon_c$ above which the vesicle
doublet cannot stay bound under a given adhesion potential.  Therefore,
the dependence of the critical extension rate $\dot\epsilon_c$ on the
adhesion potential and the mechanical vesicle properties provides a
means to probe the physics of membrane adhesion.

@@

Figure~\ref{fig:extensional1} shows snapshots from simulating a vesicle
doublet of reduced area  $\Delta A = 0.7$ at three different extension
rates. A general feature of the doublet dynamics is that the doublet
rotates from $\theta=\pi$ configuration towards the more stable
$\theta=\pi/2$ configuration.  We also observe that with moderate
extension rates, the doublet falls short of aligning their long axis
with the diverging direction.  Moreover, the final inclination angle is
closest to the stable $\theta=\pi/2$ for the smallest extension rates.
While this doublet remains bound for all the considered extension rates,
a doublet with a reduced area of $\Delta A = 0.8$ is split with a
critical extension rate $\dot\epsilon_c = 0.1$
(Figure~\ref{fig:extensional3}).

@@

The equilibrium configuration for low extension rate $\dot\epsilon=0.02$
(top row in Figure~\ref{fig:extensional1}) is almost identical to the
equilibrium configuration for $\Delta y=0$ (top row of
Figure~\ref{fig:extensionalNonsymmetric}).  The rotation of the vesicle
doublet from $\theta=\pi$ to $\theta=\pi/2$ can be understood as the
transition from an unstable configuration $\theta=\pi$ to a stable
configuration $\theta=\pi/2$.  For higher extension rates (second and
third rows in Figure~\ref{fig:extensional1}) the partially rotated
vesicle pairs at equilibrium are also very similar to the case of
$\Delta y=0.02$ (second row of
Figure~\ref{fig:extensionalNonsymmetric}).  Such asymmetric vesicle
configuration is reminiscent of the asymmetric deformation of a single
vesicle in an extensional flow~\cite{KantslerSegreSteinberg2008_PRL,Narsimhan2014_JFM,DahlNarsimhanGouveia2016_SoftMatt}.
To gain more insight into such nonlinear dynamics, in the following we
explore more physical characterization of the transition from
$\theta=\pi$ to $\theta=\pi/2$ at different reduced area and extension
rate.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a planar shear flow}
\label{sec:sflow} 
We consider two vesicles suspended in the planar shear flow $\uu =
\dot\gamma(y,0)$, where $\dot\gamma$ is the shear rate.  To be
consistent with simulations in previous sections, the vesicles have a
length of $2\pi$ for all reduced areas.  The initial placement of the
vesicles is chosen so that the flow dives them towards one another in a
head-on collision.  In the absence of adhesion, once the vesicles are
sufficiently close, they are deflected to opposite sides of the $y$
axis, pass one another, and then separate. This head-on collision
process of two vesicles or capsules in a planar shear flow is found to
be similar between two-~\cite{LacMorelBarthes-Biesel2007_JFM,
RahimianVeerapaneniBiros2010_JCP} and
three-dimensions~\cite{LacBarthes-Biesel2008_PoF,
OmoriIshikawaImaiYamaguchi2013_JBiomechics,
RahimianVeerapaneniZorinBiros2015_JCP}.  However, in the presence of
adhesion, the vesicles can form a doublet for certain values of the
separation distance $\delta$, Hamaker constant $\mathcal{H}$, shear rate
$\dot\gamma$, and reduced area $\Delta A$.  If a doublet does form, then
it undergoes a periodic motion with a period that depends on the same
parameters.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{sec:conclusions}}
\todo[inline]{conclusions need touched up}
In this work we use a boundary integral formulation with adaptive
time-stepping to simulate hydrodynamics of two vesicles with adhesive
interactions.  In a quiescent flow, two vesicles that are initially
sufficiently far apart move towards each other under a long-range
attraction.  We use a lubrication theory to estimate the time required
to reach the separation distance $\delta$, and the theoretical scaling
is in good agreement with numerical results.  Once two membranes are
within separation distance $\delta$, the adhesive force turns repulsive
and the membranes flatten to form a contact region.  Our simulations
show that the membranes in the contact region are actually curved with
end points at the shortest distance.  Once a vesicle doublet forms, we
examine the dependence of membrane bending and adhesion energies on the
reduced area, the Hamaker constant, and the separation distance.
